Article Title

### 2013-07-31 sections/Theory.tex
small changes

Let $x_i \in \mathcal X, i=1\ldots,x_n$ denote a sample of consequtive observations of population activity of $p$ neurons in time bins $i$.  
The activity of each neuron is the real-valued firing rate \TODO{Need to define rate more precisely}, thus  $\mathcal X = \mathbb R^{p\times 1}$.  
We assume that observations are drawn from some true cumulative probability distribution $F: \mathcal X \mapsto R$. Then let $\hat F_n$ denote the empirical distribution function obtained from the observed sample, which itself is a random variable.
\begin{equation}
\hat F_n(x) = \frac 1 n \sum\limits_{i=1}^n \mathbf{1}(x \ge x_i)
\end{equation}
where $\mathbf 1(x \ge x_i)$ is the indicator function which equals 1 when all elements of $x$ are greater than the corresponding elements of $x_i$ and 0 otherwise. \TODO{Are you using cumulative distributions to avoid binning?}

@@

When the loss function is the error sum of squares, which, for matrices, is called the Frobenius norm, 
\begin{equation}
\mathcal L_e(\hat S,S) = \|\hat S-S\|_F^2 = \Tr\left((\hat S-S)(\hat S-S)^\T\right)
\end{equation}
the bias-variance decomposition is the simple sum
\begin{equation}
r_\gamma =  b_\gamma^2 + \varepsilon_\gamma^2
\end{equation}

@@

Regularization is the game of minimizing risk $r_\gamma$ by reducing estimation error $\varepsilon_\gamma$ at the cost of increased bias $b_\gamma$, the \emph{bias-variance tradeoff}.  \TODO{This point can be untuitive.  For example, \cite{Varoquaux:2012} misrepresents the effect of regularization by stating that regularization removes the upward bias of correlations in the sample covariance matrix. In reality, regularization should start with an unbiased estimator and bias it toward a low-variance target so that the estimation risk is reduced. Another important point is ``Stein's paradox'': regularization does not improve the estimate of each covariance. In fact, it makes it worse. Regularization only improves the risk when measured on the entire matrix. Regularization should not be used to improve the estimate of average correlations or the distribution of correlations.}
We follow the convention that $\hat\Sigma_{\gamma=0}$ is the unbiased estimator $\hat\Sigma_0$, \emph{i.e.}\;$b_{\gamma=0}^2 = 0$.  Then as $\gamma$ increases, $\hat\Sigma_\gamma$ less variable but increasingly biased.  Thus $\hat\Sigma_\gamma$ defines the \emph{regularization path}, for which \emph{regularization intensity} $\gamma$ specifies the location along the path, which may be real-valued or discrete, or even a vector to steer the bias toward multiple targets.

>>>>

Let $x_i \in \mathcal X, i=1\ldots,x_n$ denote a sample of consequtive observations of population activity of $p$ neurons in time bins $i$.  
The activity of each neuron is the real-valued firing rate \TODO{Need to define rate more precisely}, thus  $\mathcal X = \mathbb R^{p\times 1}$.  
We assume that observations are drawn from some true cumulative probability distribution $F: \mathcal X \mapsto R$. Then let $\hat F_n$ denote the empirical distribution function obtained from the observed sample, which itself is a random variable.
\begin{equation}
\hat F_n(x) = \frac 1 n \sum\limits_{i=1}^n \mathbf{1}(x \ge x_i)
\end{equation}
where $\mathbf 1(x \ge x_i)$ is the indicator function which equals 1 when all elements of $x$ are greater than the corresponding elements of $x_i$ and 0 otherwise. \TODO{KJ: Are you using cumulative distributions to avoid binning? DY: Yes. Many theorems such as Glivenko-Catelli Theorem and Skorohod's Representation are proven using  cumulative representation. The empirical distribution is nearly always represented in its cumulative form. Expressing convergence is requires binning or using cumulative; the latter is simpler.}

@@

When the loss function is the error sum of squares, which, for matrices, is called the Frobenius norm, 
\begin{equation}
\mathcal L_e(\hat S,S) = \|\hat S-S\|_F^2 = \Tr\left((\hat S-S)(\hat S-S)^\T\right)
\end{equation}
the variance-bias decomposition is the simple sum
\begin{equation}
r_\gamma =  b_\gamma^2 + \varepsilon_\gamma^2
\end{equation}

@@

Regularization is the game of minimizing risk $r_\gamma$ by reducing estimation error $\varepsilon_\gamma$ at the cost of increased bias $b_\gamma$, the \emph{bias-variance tradeoff}.  \TODO{This point can be untuitive.  For example, \cite{Varoquaux:2012} misrepresents the effect of regularization by stating that regularization removes the upward bias of correlations in the sample covariance matrix. In reality, regularization should start with an unbiased estimator and bias it toward a low-variance target so that the estimation risk is reduced. Another important point is ``Stein's paradox'': regularization does not improve the estimate of each covariance. In fact, it makes it worse. Regularization only improves the risk when measured on the entire matrix. Regularization should not be used to improve the estimate of average correlations or the distribution of correlations.}
We follow the convention that $\hat\Sigma_{\gamma=0}$ is the unbiased estimator $\hat\Sigma_0$, \emph{i.e.}\;$b_{\gamma=0}^2 = 0$. 
We define a sequence of approximations $\hat\Sigma_\gamma$ that become less variable as as $\gamma$ increases, which is usually accompanies by increased bias. Then $\hat\Sigma_\gamma$ defines the \emph{regularization path}, for which \emph{regularization intensity} $\gamma$ specifies the location along the path, which may be real-valued or discrete, or even a vector to steer the bias toward multiple targets.

An unbiased estimate does not guarantee lack of bias in nonlinear functions of that estimate: $\mathbb E\left[\hat\Sigma_0\right]=0 \centernot\implies  E\left[\varphi(\hat\Sigma_0\right)]=0$, where $\varphi$ is a nonlinear function.
